---
title: "Analyses and Plots for Experiments 1, 2, & 3 in Özkan & Störmer (2024)"
author: "Mert Özkan"
output:
  html_document:
    df_print: paged
---

# Load Libraries
```{r}
library(tidyverse)
library(ggplot2)
options(dplyr.summarise.inform = FALSE)
setwd("~/Dropbox (Dartmouth College)/DataCollection/multifocal_analys")
save.path <- "~/Dropbox (Dartmouth College)/Manuscripts/Multifocal Attention/"

f_sep <- .Platform$file.sep
pwt_cd <- function(df,fml){
  # pairwise t test and cohen's d
  t <- rstatix::pairwise_t_test(df, fml, paired=T)
  d <- rstatix::cohens_d(df, fml, paired=T)
  t$effsize <- d$effsize
  t$magnitude <- d$magnitude
  return(t)
  
}

shape_order <- c("Narrow","Broad","Split")
```

```{r}
char2num <- function(char){
  
  i = 1
  num = rep(0,length(char))
  for(charN in unique(char)){
    
    isCharN = char==charN
    num[isCharN] = i
    i = i + 1
  }
  
  return(as.factor(num))
}

read.csv('wi_multifocal_raw_groupN30.csv') %>%
  rename(Focus=Shape) %>%
  mutate(Focus = replace(Focus, Focus=="Single", "Narrow"),
         Focus = factor(Focus,levels = shape_order)) %>%
  filter(!(Participant %in% c("JS","EGT", "NH"))) %>%
  mutate(Participant = char2num(Participant)) %>%
  select(c(Participant, Side, Focus, CueLocation, isTarget, Target_Type, ProbeLocation, ExactLocation, Accuracy)) %>%
  write.csv("./data/clean/exp1_multifocal_clean.csv")
```

# Experiment 1

1. Load participant data

```{r}
exp1 <- read.csv('wi_multifocal_raw_groupN30.csv') %>%
  rename(Focus=Shape) %>%
  mutate(Focus = replace(Focus, Focus=="Single", "Narrow"),
         Focus = factor(Focus,levels = shape_order))
head(exp1)
```
2. Find participants with more than 25% of trials discarded due to eye movements
```{r}
exp1.overall_accuracy <- exp1 %>%
  group_by(Participant) %>%
  dplyr::summarize(proportion_correct = mean(Accuracy),
                   no_of_trials = length(Accuracy),
                   pc_trials = 100*no_of_trials/720,
                   isLessThan75PC = pc_trials < 75
                       )

exp1.excluded <- c("EGT","NH")
exp1.overall_accuracy %>%
  filter(isLessThan75PC)
```

3. Contrast thresholds: find the outliers
```{r}
exp1.sub <- unique(exp1$Participant)
rawdatapath <- "../multifocal_eyetracker/data/raw/behavioral/"
rawdatafiles <- Sys.glob(sprintf("%s%smfet_main_bhv*%s_*.csv",rawdatapath,f_sep,exp1.sub))


exp1.excluded <- c(exp1.excluded, "JS")
```

3. Filter out the excluded participants

```{r}
exp1 <- exp1 %>% filter(!(Participant %in% exp1.excluded))
n_sub <- length(unique(exp1$Participant))
```
27 participants left.

4. Violin plot of accuracies

```{r}


exp1.processed <- exp1 %>%
  mutate(Cue = as.character(Target_Type)) %>%
  dplyr::group_by(Participant,Focus,Cue) %>%
  dplyr::summarize(proportion_correct = mean(Accuracy),
                       no_of_trials = length(Accuracy))

exp1.summary <- exp1.processed %>%
  Rmisc::summarySEwithin(measurevar = "proportion_correct",
                withinvars = c("Focus","Cue"),
                idvar = c("Participant")
                )

exp1.summary

ggplot(
  exp1.processed,
  aes(x = Cue,y=proportion_correct,fill=Cue)) +
  geom_hline(yintercept = .5) +
  geom_point(color='grey')+
  geom_violin(alpha=.5,trim=T,color=NA) +
  geom_errorbar(data = exp1.summary,
                aes(ymin=proportion_correct-se,ymax=proportion_correct+se),width=.1) +
  geom_point(data=exp1.summary) +
  facet_wrap(~ Focus, scales='free_x') +
  coord_cartesian(ylim = c(.4,1)) +
  guides(fill='none') + ylab('Proportion of Correct Responses') +
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, hjust=.5))
```
## Main ANOVA (Table 1)

1. Reduce cue conditions to two levels
```{r}
exp1.aov.df <- exp1 %>%
  mutate(Cue = as.character(Target_Type)) %>%
  mutate(Cue = replace(Cue,Cue %in% c("Outer_Uncued","Intermediate_Uncued"),'Uncued')) %>%
  dplyr::group_by(Participant,Focus,Cue) %>%
  dplyr::summarize(proportion_correct = mean(Accuracy),
                       no_of_trials = length(Accuracy)) %>%
  ungroup() %>% droplevels()
head(exp1.aov.df)
```
2. Two—way ANOVA

```{r}
exp1.aov <- rstatix::anova_test(data=exp1.aov.df,
                                  formula = proportion_correct ~ Focus * Cue + Error(Participant/Focus * Cue),
                                  effect.size = 'pes')
exp1.aov
```
ANOVA results indicate only a significant main effect of Cue condition.

2.1 Bayes Factor Analysis

```{r}
set.seed(42)
exp1.bf.aov <- BayesFactor::anovaBF(data= exp1.aov.df%>%
                       mutate(Participant = factor(Participant),
                              Cue = factor(Cue),
                              Focus = factor(Focus)
                              ),
                     formula= proportion_correct ~ Focus * Cue+ Participant, whichRandom = 'Participant')

exp1.bf.aov
```
BF(Cue) = 8304.2

Adding Focus to the model:
```{r}
exp1.bf.aov[3]/exp1.bf.aov[2]
```
BF(Focus) = BF(Focus + Cue) / BF(Cue) = .1

Adding the interaction term
```{r}
exp1.bf.aov[4]/exp1.bf.aov[3]
```
BF(Focus:Cue) = BF(Focus + Cue + Focus:Cue) / BF(Focus + Cue) = 0.31

## Post—Hoc Pairwise T—Tests (Table 2)

1. Pairwise T-Tests
```{r}
exp1.processed %>%
  group_by(Focus) %>%
  group_modify(~pwt_cd(.,proportion_correct ~ Cue)) %>% ungroup() %>%
  rstatix::adjust_pvalue(p.col = "p", method="BH")
  
```
2. Bayes Factors associated with post-hoc t-tests
```{r}
exp1.pht_bf <- exp1.processed %>%
  select(-no_of_trials) %>%
  spread(Cue,proportion_correct)


sprintf("Narrow (Cued v Outer Uncued)")
datN <- exp1.pht_bf %>%
  filter(Focus == "Narrow") 
set.seed(46)
BayesFactor::ttestBF(x = datN$Cued, y=datN$Outer_Uncued, paired = T)

sprintf("Broad (Cued v Outer Uncued)")
datN <- exp1.pht_bf %>%
  filter(Focus == "Broad") 
set.seed(46)
BayesFactor::ttestBF(x = datN$Cued, y=datN$Outer_Uncued, paired = T)

sprintf("Split (Cued v Outer Uncued)")
datN <- exp1.pht_bf %>%
  filter(Focus == "Split") 
set.seed(46)
BayesFactor::ttestBF(x = datN$Cued, y=datN$Outer_Uncued, paired = T)

sprintf("Split (Cued v Intermediate Uncued)")
datN <- exp1.pht_bf %>%
  filter(Focus == "Split") 
set.seed(46)
BayesFactor::ttestBF(x = datN$Intermediate_Uncued, y=datN$Cued, paired = T)

sprintf("Split (Intermediate Uncued v Outer Uncued)")
datN <- exp1.pht_bf %>%
  filter(Focus == "Split") 
set.seed(46)
BayesFactor::ttestBF(x = datN$Intermediate_Uncued, y=datN$Outer_Uncued, paired = T)

```
3. Comparing performance at corresponding locations in the broad— and split—focus conditions

```{r}
exp1.pht.loc <- exp1 %>%
  # Collapse left and right sides
  mutate(ExactLocation = replace(ExactLocation, ExactLocation > 90, 
                                 180 - ExactLocation[ExactLocation > 90])) %>%
  filter(Focus != "Narrow" &
           !(ExactLocation %in% c(36, 54))
           ) %>%
  group_by(Participant, Focus, ExactLocation,Target_Type) %>%
  summarise(proportion_correct = mean(Accuracy),
            no_of_trials = length(Accuracy),
            ) %>%
  rename(Cue = Target_Type)

head(exp1.pht.loc)

exp1.pht.loc %>%
  Rmisc::summarySEwithin(
    withinvars = c("ExactLocation", "Focus"),
    measurevar = "proportion_correct",
    idvar = "Participant"
  )

```
```{r}
exp1.pht.loc %>%
  group_by(ExactLocation) %>% droplevels() %>%
  group_modify(~pwt_cd(., proportion_correct ~ Focus)) %>%
  ungroup() %>%
  rstatix::adjust_pvalue(p.col = "p", method="BH")
```
The intermediate location (ExactLocation = 45) did not differ significantly between focus condition even though it is cued in the broad and uncued in the split condition
```{r}
datN <- exp1.pht.loc %>%
  filter(ExactLocation == 45) %>%
  select(-c(Cue, no_of_trials)) %>%
  spread(Focus, proportion_correct)


set.seed(46)
BayesFactor::ttestBF(x = datN$Broad, y=datN$Split, paired = T)
  
```
Bayes factor is above 1, indicating that there is high likelihood of a false negative result.

# Experiment 2
```{r}
exp2.bhv = read.csv('./ssvep_exp1_bhv.csv') %>%
  rename(Focus=Shape,
         Participant=sub) %>%
  mutate(Focus = replace(Focus, Focus=="Single", "Narrow"),
         Focus = factor(Focus,levels = shape_order))
head(exp2.bhv)
exp2.snr = read.csv('./ssvep_exp1_snr_N31.csv') %>%
  rename(Focus=shape,
         Participant=participant) %>%
  mutate(Focus = replace(Focus, Focus=="Single1", "Narrow1"),
         Focus = replace(Focus, Focus=="Single2", "Narrow2"))
head(exp2.snr)

exp2.stim_freqs = 120/c(9,10,11)
```
## Participant rejection
Only one participant (Sub#) was rejected due to not showing clear peaks in SNR at stimulation frequencies.
```{r}
exp2.snr %>%
  group_by(Participant,frequency) %>%
  summarise(snr = mean(snr)) %>%
  group_by(Participant) %>%
  ggplot(aes(x=frequency,y=snr)) +
  geom_vline(xintercept = exp2.stim_freqs,color='grey',alpha=.5) +
  facet_wrap(~Participant)+
  geom_line(size=.5) +coord_cartesian(xlim = c(8.24,16))
```
```{r}
exp2.exclude <- c("CJT")
```


## Behavioral Data Analysis
```{r}
get_rate <- function(detection,isTarget,level){
  return(
    (sum(detection==level,na.rm=T)+.5)/(sum(isTarget,na.rm = T,na.rm=T)+1)
  )
}
  


exp2.bhv_proc <- exp2.bhv %>% 
  filter(!Participant %in% exp2.exclude) %>%
  filter(isProbe=='True') %>%
  group_by(Participant,Focus) %>%
  summarise(
    'Hit_Rate' = get_rate(detection,isTarget,'Hit'),
    'FA_Rate' = get_rate(detection,isTarget,'FA'),
  ) %>%
  mutate(dprime = qnorm(Hit_Rate) - qnorm(FA_Rate)
         ) %>%
  select(c('Participant','Focus',"dprime")) %>%
  droplevels()

head(exp2.bhv_proc)



exp2.bhv_summ <- exp2.bhv_proc %>%
  droplevels() %>%
  Rmisc::summarySEwithin(
        measurevar = 'dprime',
        idvar = 'Participant',
        withinvars = 'Focus'
      )
head(exp2.bhv_summ)


ggplot(mapping = aes(x = Focus, y=dprime, fill=Focus)) +
  geom_point(data = exp2.bhv_proc,color='grey')+
  geom_violin(data=exp2.bhv_proc, alpha=.5,trim=T,color=NA) +
  geom_errorbar(data=exp2.bhv_summ, aes(ymin=dprime-se,ymax=dprime+se),width=.1)+
  geom_point(data=exp2.bhv_summ) +
  guides(fill='none') + ylab('dprime') + coord_cartesian(ylim= c(0,5)) 
```
1. One-way ANOVA results
```{r}
exp2.bhv_proc %>% ungroup() %>%
  rstatix::anova_test(dv = "dprime", within = "Focus", wid = "Participant", effect.size = "pes")
```
2. Bayes Factor analysis on the ANOVA results
```{r}
set.seed(42)
exp2.bhv.bf.aov <- BayesFactor::anovaBF(data= exp2.bhv_proc%>%
                       mutate(Participant = factor(Participant),
                              Focus = factor(Focus)
                              ),
                     formula= dprime ~ Focus + Participant, whichRandom = 'Participant')

exp2.bhv.bf.aov
```
3. Post—Hoc T—Tests
```{r}
exp2.bhv_proc %>% ungroup() %>%
  pwt_cd(dprime ~ Focus)
```
4. Bayes Factors on Post—Hoc T—tests
```{r}
exp2.bhv.pht_bf <- exp2.bhv_proc %>%
  spread(Focus,dprime)


sprintf("Narrow v Broad")
set.seed(46)
BayesFactor::ttestBF(x = exp2.bhv.pht_bf$Narrow, y=exp2.bhv.pht_bf$Broad, paired = T)

sprintf("Narrow v Split")
set.seed(46)
BayesFactor::ttestBF(x = exp2.bhv.pht_bf$Narrow, y=exp2.bhv.pht_bf$Split, paired = T)

sprintf("Split v Broad")
set.seed(46)
BayesFactor::ttestBF(x = exp2.bhv.pht_bf$Split, y=exp2.bhv.pht_bf$Broad, paired = T)
```
## SSVEP Results
1. Process data
```{r}
find_local_max <- function(df,foi,n_search_bin = 2){
  
  fq <- c()
  snr <- c()
  lbl <- c()
  
  for(whFoi in 1:length(foi)){
  
    foiN = foi[whFoi]
    search_idx <- which.min(abs(df$frequency-foiN)) + -n_search_bin:n_search_bin
    max_idx <- search_idx[which.max(df$snr[search_idx])]
    fq <- rbind(fq,df$frequency[max_idx])
    snr <- rbind(snr,df$snr[max_idx])
    lbl <- rbind(lbl,round(foiN)) #rbind(lbl,sprintf("%d",round(foi[whFoi])))
      
  }
  
  return(data.frame(frequency=lbl,exact_frequency=fq,snr) %>% ungroup())
  
}

exp2.get_ai <- function(df){
  
  new_df <- c()
  for(foiN in unique(df$frequency)){
    
    if(foiN == 12){
        
        comparison_cond = "Narrow1"
        
        
      }else{
        
        comparison_cond = "Narrow2"
        
      }
    
      new_df <- rbind(new_df,
                    df %>%
                      filter(frequency == foiN) %>%
                      mutate(ai = snr/((snr+snr[Focus == comparison_cond])/2)) %>%
                      filter(Focus != comparison_cond) %>%
                      mutate(Focus = as.character(Focus),
                             Focus = factor(
                        replace(Focus, Focus %in% c("Narrow1","Narrow2"),"Narrow")))
      )
                    
  }
  return(new_df)
}


exp2.ai <- exp2.snr %>%
  filter(!(Participant %in% exp2.exclude)) %>%
  group_by(Participant,Focus) %>%
  group_modify(~find_local_max(.,foi = exp2.stim_freqs)) %>%
  ungroup() %>%
  group_by(Participant) %>%
  group_modify(~ exp2.get_ai(.))%>%
  mutate(shape = factor(Focus,levels = c('Narrow','Split','Broad'))) %>%
  filter(frequency != 13)

head(exp2.ai)


exp2.ai.summary <- exp2.ai %>%
  droplevels() %>%
  Rmisc::summarySEwithin(
        measurevar = 'ai',
        idvar = 'Participant',
        withinvars = c('Focus',"frequency")
      )
head(exp2.ai.summary)


```
2. T—tests to determine whether there were successful attentional modulations
```{r}
exp2.ai %>%
  group_by(Focus, frequency) %>%
  rstatix::t_test(ai ~ 1, alternative = "greater", mu=1) %>%
  rstatix::add_significance()
```

3. Two—way ANOVA Results
```{r}
exp2.ai %>% ungroup() %>%
  rstatix::anova_test(dv = "ai", within = c("Focus","frequency"), wid = "Participant", effect.size = "pes")
```
4. Bayes Factor on ANOVA
```{r}
set.seed(42)
exp2.ai.bf.aov <- BayesFactor::anovaBF(data= exp2.ai%>%
                       mutate(Participant = factor(Participant),
                              Focus = factor(Focus),
                              frequency = factor(frequency)
                              ) %>% ungroup(),
                     formula= ai ~ Focus * frequency + Participant, whichRandom = 'Participant')

exp2.ai.bf.aov
```
BF for "frequency"
```{r}
exp2.ai.bf.aov[3]/exp2.ai.bf.aov[1]
```
BF for "interaction"
```{r}
exp2.ai.bf.aov[4]/exp2.ai.bf.aov[3]
```
5. PostHoc T—tests
```{r}
exp2.ai %>% ungroup() %>%
  group_by(Participant, Focus) %>%
  summarise(ai = mean(ai)) %>%
  ungroup() %>%
  pwt_cd(ai ~ Focus)
```
6. Bayes Factors on Post—Hoc T—tests
```{r}
exp2.ai.pht_bf <- exp2.ai %>% ungroup() %>%
  group_by(Participant, Focus) %>%
  summarise(ai = mean(ai)) %>%
  spread(Focus,ai)


sprintf("Narrow v Broad")
set.seed(46)
BayesFactor::ttestBF(x = exp2.ai.pht_bf$Narrow, y=exp2.ai.pht_bf$Broad, paired = T)

sprintf("Narrow v Split")
set.seed(46)
BayesFactor::ttestBF(x = exp2.ai.pht_bf$Narrow, y=exp2.ai.pht_bf$Split, paired = T)

sprintf("Split v Broad")
set.seed(46)
BayesFactor::ttestBF(x = exp2.ai.pht_bf$Split, y=exp2.ai.pht_bf$Broad, paired = T)
```
# Experiment 3
```{r}
exp3.bhv = read.csv('./ssvep_exp2_bhv_N24.csv') %>%
  rename(Focus=Shape) %>%
  mutate(Focus = replace(Focus, Focus=="S", "Split"),
         Focus = replace(Focus, Focus=="B", "Broad"))
head(exp3.bhv)
exp3.snr = read.csv('./ssvep_exp2_snr_N24.csv') %>%
  rename(Focus=shape,
         Participant=participant)
head(exp3.snr)

exp3.stim_freqs =  120/c(9,10,11,13,15,17)
```
## Behavioral Results
1. Process data, summarize, and plot
```{r}
get_summary <- function(df){
  return(
    df %>%
      Rmisc::summarySEwithin(
        measurevar = 'value',
        idvar = 'Participant',
        withinvars = 'Focus',na.rm = T
      )
  )
}

get_rate.exp3 <- function(Response,EventType,var,resp){
  return(
    (sum(Response %in% resp)+.5)/(sum(EventType %in% var)+1)
  )
}

exp3.bhv_proc <-exp3.bhv %>%
  group_by(Participant,Focus) %>%
  summarise(
    'Hit Rate' = get_rate.exp3(Response,EventType,'TAR','HIT'),
    'False Alarm Rate (Similar)' = get_rate.exp3(Response,EventType,'DIS','SFA'),
            ) %>%
  reshape2::melt(id=c('Participant','Focus')) %>%
  rename(metric=variable) %>%
  mutate(thresholded = T) %>%
  mutate(thresholded = replace(thresholded, Participant %in% c(1,2,3,7),F)) %>%
  filter(Focus %in% c("Broad", "Split"))

exp3.bhv.summary <- exp3.bhv_proc %>%
  group_by(metric) %>%
  group_modify(~get_summary(.))
exp3.bhv.summary
```
```{r}
ggplot(
  exp3.bhv.summary,
  aes(x = Focus,y=value,fill=Focus)) +
  geom_point(data = exp3.bhv_proc,color='grey')+
  geom_violin(data = exp3.bhv_proc,alpha=.5,trim=T,color=NA) +
  geom_errorbar(aes(ymin=value-se,ymax=value+se),width=.1)+ geom_point() +
  facet_wrap(~ metric) +
  guides(fill='none') + ylab('Proportion of Positive Response') + coord_cartesian(ylim = c(0,1))
```
2. T-Test on Hits and FAs
```{r}
exp3.bhv_proc %>%
  group_by(metric) %>%
  pwt_cd(value ~ Focus) %>%
  rstatix::adjust_pvalue(p.col="p")
```
3. Bayes Factor Analysis on the *t*—tests
```{r}
exp3.bhv.pht_bf <- exp3.bhv_proc %>% ungroup() %>%
  mutate(Focus = interaction(Focus,metric)) %>%
  select(Participant, Focus, value) %>%
  spread(Focus,value)
exp3.bhv.pht_bf

sprintf("Hit Rate")
set.seed(46)
BayesFactor::ttestBF(x = exp3.bhv.pht_bf$`Broad.Hit Rate`, y=exp3.bhv.pht_bf$`Split.Hit Rate`, paired = T)


sprintf("False Alarm Rate")
set.seed(46)
BayesFactor::ttestBF(x = exp3.bhv.pht_bf$`Broad.False Alarm Rate (Similar)`, y=exp3.bhv.pht_bf$`Split.False Alarm Rate (Similar)`, paired = T)
```
## Thresholding

## SSVEP Results

1. Process data, summary statistics and plot
```{r}
get_ai.exp3 <- function(snr,frequency,AttendedFrequency){
  
  nominator = 'Low'
  denominator = 'High'
  
  if(frequency[1] > 10){
    
    nominator = 'High'
    denominator = 'Low'
    
  }
  isNom <- AttendedFrequency==nominator
  isDnom <- AttendedFrequency==denominator
  x <-snr[isNom]/((snr[isDnom]+snr[isNom])/2)

  return(mean(x))
}

exp3.ai <- exp3.snr %>%
  filter(frequency<20) %>%
  separate(Focus,c('HighFreqSide','CueSide','Focus')) %>%
  mutate(AttendedFrequency = 'High') %>%
  mutate(AttendedFrequency = replace(AttendedFrequency,
                                     (HighFreqSide=='HL' & CueSide =='CR') |
                                       (HighFreqSide=='HR' & CueSide =='CL'),
                                     'Low')
         ) %>%
  group_by(Participant,AttendedFrequency,Focus) %>%
  group_modify(~ find_local_max(.,foi = exp3.stim_freqs)) %>%
  dplyr::group_by(Participant,Focus,frequency) %>%
  dplyr::summarize(ai = get_ai.exp3(snr,frequency,AttendedFrequency)) %>%
  mutate(AttendedFrequency =  'High') %>%
  mutate(AttendedFrequency =  replace(AttendedFrequency, frequency < 10, 'Low')) %>%
  mutate(frequency= as.numeric(as.character(frequency))) %>%
  group_by(Participant,Focus) %>%
  mutate(Location = 'OuterMost') %>%
  mutate(Location = replace(Location, frequency == 11 | frequency == 9, 'InnerMost')) %>%
  mutate(Location = replace(Location, frequency == 12 | frequency == 8, 'Intermediate')) %>%
  group_by(Participant,Focus,Location) %>%
  summarize(ai = mean(ai))

exp3.ai.summary <- exp3.ai %>%
  Rmisc::summarySEwithin(
    measurevar = 'ai',
    withinvars = c('Location','Focus'),
    idvar = 'Participant'
  )

sub_datN <- exp3.ai
summ_datN <- exp3.ai.summary
ggplot(
  summ_datN,
  aes(x = Location,y=ai,fill=Location)) +
  geom_hline(yintercept = 1) +
  geom_point(data = sub_datN,aes(x=Location),color='grey')+
  geom_violin(data = sub_datN, aes(x=Location), alpha=.5,trim=T,color=NA) +
  geom_errorbar(aes(ymin=ai-se,ymax=ai+se),width=.1)+ geom_point() +
  facet_wrap(~ Focus) +
  coord_cartesian(ylim = c(.4,2.25)) +
  guides(fill='none') + ylab('Attention Index')

head(exp3.ai.summary)
```
2. Series of T—tests per location to test whether the AI are above baseline of 1
```{r}
exp3.ai %>%
  group_by(Focus, Location) %>%
  rstatix::t_test(ai ~ 1, alternative = "greater") %>%
  rstatix::adjust_pvalue(p.col="p")
```
3. ANOVA test
```{r}
exp3.ai %>% ungroup() %>%
  rstatix::anova_test(dv = 'ai', wid = 'Participant', within = c("Focus","Location"), effect.size = "pes")
```
4. Bayes Factor Analysis on ANOVA
```{r}
set.seed(42)
exp3.ai.bf.aov <- BayesFactor::anovaBF(data= exp3.ai%>%
                       mutate(Participant = factor(Participant),
                              Focus = factor(Focus),
                              Location = factor(Location)
                              ) %>% ungroup(),
                     formula= ai ~ Focus * Location + Participant, whichRandom = 'Participant')

exp3.ai.bf.aov
```
BF for "Focus"
```{r}
exp3.ai.bf.aov[3]/exp3.ai.bf.aov[2]
```
BF for "Interaction"
```{r}
exp3.ai.bf.aov[4]/exp3.ai.bf.aov[3]
```
5. Post—Hoc T—Tests
```{r}
exp3.ai %>%
  group_by(Participant, Location) %>%
  summarise(ai = mean(ai)) %>% ungroup() %>%
  pwt_cd(ai ~ Location)
```
6. Bayes Factor Analysis on T—tests

```{r}
exp3.ai.pht_bf <- exp3.ai %>%
  group_by(Participant, Location) %>%
  summarise(ai = mean(ai)) %>% ungroup() %>%
  select(Participant, Location, ai) %>%
  spread(Location,ai)
exp3.ai.pht_bf

sprintf("Intermediate v Innermost")
set.seed(46)
BayesFactor::ttestBF(x = exp3.ai.pht_bf$InnerMost, y=exp3.ai.pht_bf$Intermediate, paired = T)

sprintf("Outermost v Innermost")
set.seed(46)
BayesFactor::ttestBF(x = exp3.ai.pht_bf$InnerMost, y=exp3.ai.pht_bf$OuterMost, paired = T)

sprintf("Intermediate v Outermost")
set.seed(46)
BayesFactor::ttestBF(x = exp3.ai.pht_bf$OuterMost, y=exp3.ai.pht_bf$Intermediate, paired = T)
```














